\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-07-22 tex/overview.tex
clarify introduction to derivation section

In the general case of a dynamical system with $n$ variables, where the variables may be concentrations of chemical species, genes, or biological species, we have an $n$-dimensional vector of state variables or observables $(x_1(t), \ldots x_n(t)) = \vec{x}(t)
$
whose components are solutions to the arbitrary first order system
\begin{equation}\label{eq:eom}
\frac{dx_i(t)}{dt} = F_i(\vec{x}(t), \vec{p}), \; (i=1,\ldots,n)
\end{equation}
where $F=\{F_1,\ldots,F_i,\ldots,F_n\}$ represent, potentially nonlinear, functions of the given vector of state variables and $\vec{p} \in \mathbb{R}^{n'}$ is the vector of $n'$ parameters of the $F_i$. These parameters typically represent reaction rates or interaction strengths in chemical, gene-regulatory and ecological networks. For example, in the Lotka-Volterra model in \ref{fig:biomodelexamples}, $\vec{x} = (x_1, \ldots, x_n)$, $\vec{p}=(r_1,\ldots,r_n,b_{11},\ldots,b_{nn})$, and $F_i = r_i x_i + \sum_{j=1}^{n} b_{ij} x_i x_j$. The set of all dynamical systems, $\mathcal{D}'$, for a given number of state variables $n$ and a given number of parameters $n'$, is then
\begin{equation}\label{eq:setdynsys}
\mathcal{D}' = \{ (F(-,\vec{p}),\vec{p}) | F \colon \mathbb{R}^n \times \mathbb{R}^{n'} \rightarrow \mathbb{R}^n, \vec{p} \in \mathbb{R}^s \}.
\end{equation}
The space of all possible $F$ may be too large to precisely define probabilities over, in which case it is possible to consider various subspaces $\mathcal{D} \subset \mathcal{D}'$. In some cases these may even be given by parametrized models with a single fixed form of $F$ and then varying $\vec{p}$ alone would be sufficient to vary within that class of dynamical systems.

@@

\subsection{Equivalence classes of systems associated to Jacobian Matrices}
We would ultimately like to determine the probability of a stable system remaining stable in the context of evolution modeled as a stochastic process operating on a large set of dynamical systems. Any given Jacobian matrix, which is what characterizes the stability of a system near a given fixed point, does not refer to a single dynamical system, but rather a set of fundamentally distinct dynamical systems from which that Jacobian matrix could have derived. More precisely, Jacobian matrices define an equivalence relation, $\sim$, on fixed points, $\mathcal{F}$, given by $(F,\vec{p},\vec{x}^0) \sim (F',\vec{p}\,',\vec{x}^{0'}) $ if and only if
\begin{equation}\label{eq:jaceqrel}
\left. \frac{\partial F(\vec{x},\vec{p})}{\partial \vec{x}} \right|_{\vec{x} = \vec{x}^0} =
\left. \frac{\partial F'(\vec{x},\vec{p}\,')}{\partial \vec{x}} \right|_{\vec{x} = \vec{x}^{0'}}.
\end{equation}
This relation then partitions the set of all fixed points into equivalence classes $\mathcal{F}/{\sim}$, where the class $[A]$ associated to Jacobian matrix $A \in \mathbb{R}^{n \times n}$ is
\begin{equation}\label{eq:jaceqs}
[A] = \left\{ (F,\vec{p},\vec{x}^0) \; \Bigg| \; \left. \frac{\partial F(\vec{x},\vec{p})}{\partial \vec{x}} \right|_{\vec{x} = \vec{x}^0} = A \right\}.
\end{equation}
An example with two members of $\mathcal{F}$ from each of four different equivalence classes $[A_1]$, $[A_2]$, $[A_3]$, and $[A_4]$ of $\mathcal{F}/{\sim}$ is shown in \ref{fig:robustnessconcept}.

% \subsection{Overview}
\subsection{Interaction graphs encoding network architecture}
We are interested in the manner in which system variables interact with one another, and, ultimately, whether dynamical robustness depends upon the topology of these interactions. Interactions among system variables can be encoded in a directed graph associated to the system. Strictly speaking, the interactions among variables in a dynamical model for any network can be represented in terms of a global interaction graph (\ref{fig:biomodelexamples} top row).
For a general system $X \in \mathcal{D}$ the directed graph $G_X$ that describes the manner in which each of the variables depends upon one another can be represented by the adjacency matrix $\adj(G_X)$ where $\adj(G_X)_{ij}$ is $1$ if $F_i \hbox{ depends on } x_j$ and $0$ if $F_i \hbox{ does not depend on } x_j$. These two conditions on global system interactions are expressed locally for all $\vec{x}$ in terms of elements of the Jacobian matrix as $\frac{\partial F_i}{\partial x_j}(\vec{x}) \neq 0$ and $\frac{\partial F_i}{\partial x_j}(\vec{x}) = 0$.
%  \begin{displaymath}
%    \adj(G_X)_{ij} = \left\{
%      \begin{array}{ll}
%        1, & F_i \hbox{ depends on } x_j\\
%        0, & F_i \hbox{ does not depend on } x_j
%      \end{array}.
%    \right.
% \end{displaymath}
For large systems, since any given variable is only likely to interact with a relatively small proportion of the other variables, these matrices may be sparse.
We can also associate a local interaction graph $G_A$ given by an adjacency matrix $\adj(G_A)$ to each dynamical system having Jacobian matrix $A$ at some fixed point $\vec{x}^0$ where
 \begin{equation}\label{eq:lininterdepadj}
   \adj(G_A)_{ij} = \left\{
     \begin{array}{lr}
       1, & a_{ij} \neq 0\\
       0, & a_{ij} = 0
     \end{array}.
   \right.
\end{equation}
In general, the graph $G_A$ is a subgraph of $G_X$, however, $G_A$ is equal to $G_X$, and thus $\adj(G_A) = \adj(G_X)$, for the classes of systems of interest here (see \refsupp{} \ref{sec:reactionnetjacobian}). We define the connectivity to be equal to the number of edges in $G_A$, which is equivalent to summing up the number of non-zero entries of $\adj(G_A)$.
These interaction graphs can be viewed as deriving from the combination of system components that accept a given pattern of inputs and produce a given pattern of outputs (\reffigexamplesystemmodules).

@@

\section{Evolutionary processes sampling dynamical systems}
In the course of biological evolution, the parameter values $\vec{p}$, form of the functions $F$, and environmental conditions restricting access to the basins associated to different fixed points $\vec{x}^0$ corresponding to all different types of networks considered in \ref{fig:biomodelexamples} are subject to, potentially drastic, modifications due to environmental fluctuations. The stochastic process by which these modifications occur induces one on the set of fixed points that results in the assignment of a probability $P(f^T)$ to each history of length $T$, $f^T = ( f_1,f_2,\ldots,f_T ) \in \mathcal{F}^T$ \cite{RobertM.Gray130}.
% $$
% P(f',t+1 | f,t) = \mathcal{T}_{\mathcal{F}}(f',f)
% $$
% for all $f,f' \in \mathcal{F}$.
These dynamics induce a stochastic process on the equivalence classes of fixed points $\mathcal{F}/{\sim}$ indexed by Jacobian matrices given by
$$
P([A]^T) = \sum_{ \{ f^T \mid f_i^T \in [A]_i^T \} } P(f^T)
$$
for each history of length $T$, $[A]^T = ( [A_1], [A_2], \ldots, [A_T] ) \in (\mathcal{F}/{\sim})^T$
% $$
% P([A'],t+1 | [A],t) = \mathcal{T}_{\mathcal{F}/{\sim}}([A'],[A])
% $$
% for all $A,A' \in \mathcal{F}/{\sim}$
as visualized in \ref{fig:robustnessprocess}B. These changes can alter the stability of a given system, thereby inducing an even more coarse-grained stochastic process on the stable regions of the space of fixed points given by
$$
P(s^T) = \sum_{ \{ A^T \mid \mathcal{S}(A_i^T) = s_i^T \} } P(A^T)
$$
for each history of length $T$, $s^T = ( s_1, s_2, \ldots, s_T ) \in \{0,1\}^T$ where $s=1 \equiv S,\, s=0 \equiv U$ as visualized in \ref{fig:robustnessprocess}A and B. In order to model this, we consider a process whereby perturbations applied to a given dynamical system and fixed point associated to a stable Jacobian matrix $A$ lead to another Jacobian matrix $A'$.  This corresponds to an ensemble of fixed points of dynamical systems where each model in the ensemble may otherwise be defined in terms of a different collection of rate functions $F'$, vector of parameters ${\vec{p}}\,'$, or environmental conditions restricting access to $\vec{x}^{0'}$ (\refsupp{} \ref{sec:reactionnetjacobian}). We then ask what is the probability, given $A$ is a stable matrix, that $A'$ is also a stable matrix. This quantifies the intuitive statement that, over evolutionary timescales, it is not enough for a system to be stable, but rather that it have a reasonably high probability of remaining stable over contiguous timeframes. In terms of a history $s^T$ over the states specifying the stability property, $\mathcal{S}$, this is given by
$$
r = \frac{\sum_{t=0}^{T-1} s_{t+1}^T s_{t}^T}{\sum_{t=0}^{T-1} s_{t}^T}.
$$
If the process $P(s^T)$ has limits $\mu(s) = \lim_{t,T \rightarrow \infty} P(s_t^T=s)$ and $\tau(s' \mid s) = \lim_{t,T \rightarrow \infty} P(s_{t+1}^T = s' \mid s_t^T = s)$ for $s,s' \in \{0,1\}$
%stationary probability $P^{\infty}(s)$ for $s \in \mathcal{S}$
, the expectation of $r$ as $T \rightarrow \infty$ is approximated by
\begin{equation}\label{eq:robustnessfromstoch}
R(S,\mu,\tau) = E[r] \approx \frac{\sum_{s,s'} \mu(s) \tau(s' \mid s)}{\sum_{s=1} \mu(s)}.
\end{equation}
This conditional probability corresponds to the parameter $R$ of the two-state process depicted in \ref{fig:robustnessprocess}A, and it is what we refer to as dynamical robustness.

@@

\subsection{Symmetries of SCCs and their relationship to robustness}
This map $\hier$ is many-to-one and so there is a large class of
operations which leaves $\hier(G)$ invariant for a given graph $G$ \reffighiertransformations{}. These three symmetries, \reffigscc{}, represent transformations that can be performed on the interaction graph that do not change the network of SCCs to which it is associated.
For instance, we may interchange the positions of the SCCs relative to each other \reffighiertransformations$a$.  Leaving the components fixed, we may move links between nodes in a component \reffighiertransformations$b$ or between components, or even add or delete links \reffighiertransformations$c$.

Symmetries with respect to some property of the system are characterized by the ability to interchange these modules or their connectivity without changing that property. Two of these three intrinsic symmetries of $\hier$ are also symmetries with respect to dynamical robustness. \ref{fig:robustnesssymmetries} shows an example of these latter symmetries applied to a specific interaction graph. The collections of networks that have equivalent dynamical robustness characterized by its symmetries allow for a classification of neutral networks with respect to any process in which maximal robustness is selected for.

\section{Derivation of the relationship between network architecture and robustness}
Here we show that dynamical robustness is maximized by the most hierarchical of network architectures. In doing so, we restrict to a set of graphs which has the same SCCs but may have different links between the components, consider a stochastic process as a simple model for evolution that independently resamples individual elements of Jacobian matrices, and maximize robustness in that context.

We demonstrate that the Jacobian matrix associated to a system at a fixed point is stable in the sense of \ref{eq:stabeval} if and only if each of the blocks corresponding to its SCCs are all independently stable. We derive an analytical expression for dynamical robustness, $R$, of a network in terms of its interaction graph, $G$, as a weighted average of the dynamical robustness values, $R_{\alpha}$, of the SCCs, $C_{\alpha}$, the corresponding number of links within each SCC, $d_{\alpha}$, and the number of links between the SCCs, $l$ to give a total connectivity $d = l + \sum_{\alpha} d_{\alpha}$. The network architecture having $l=l_{max}$ is the most hierarchical one. Comparing the robustness of a network architecture having $l = l_{max}$ to any other network architecture having any other value of $l$, we show that the most hierarchical network architecture maximizes dynamical robustness. The result ultimately holds for those processes involving simultaneous perturbation of any number of elements of the Jacobian. To anchor the intuition before stating the more general result, we derive the expression for the case of perturbing a single element at each timestep of the process.
\subsection{Decomposition of stability over SCCs}
Let the index $i$ range over the non-zero entries $a_i$ of $A$. The entries of the Jacobian are sampled independently from a generic probability distribution $\rho_i$ for each entry. Under this assumption then
\begin{equation}\label{eq:singleresamplemutau}
\begin{aligned}
\mu(A) &= \prod_i \rho_i(a_i),\\
\tau^{(1)}(A' \mid A) &= \frac{1}{d} \sum_i \tau^{(1)}_i (A' \mid A),
\end{aligned}
\end{equation}
where
$$
\tau^{(1)}_i(A' \mid A) = \rho_i(a'_i) \prod_{j \neq i} \delta(a'_j - a_j).
$$

>>>>

To begin our analysis we will define dynamical systems on biological networks, review the manner in which their linear stability can be evaluated and describe how each one can be associated to a graph encoding interactions among system variables. In the general case of a dynamical system with $n$ variables, where the variables may be concentrations of chemical species, genes, or biological species, we have an $n$-dimensional vector of state variables or observables $(x_1(t), \ldots x_n(t)) = \vec{x}(t)
$
whose components are solutions to the arbitrary first order system
\begin{equation}\label{eq:eom}
\frac{dx_i(t)}{dt} = F_i(\vec{x}(t), \vec{p}), \; (i=1,\ldots,n)
\end{equation}
where $F=\{F_1,\ldots,F_i,\ldots,F_n\}$ represent, potentially nonlinear, functions of the given vector of state variables and $\vec{p} \in \mathbb{R}^{n'}$ is the vector of $n'$ parameters of the $F_i$. These parameters typically represent reaction rates or interaction strengths in chemical, gene-regulatory and ecological networks. For example, in the Lotka-Volterra model in \ref{fig:biomodelexamples}, $\vec{x} = (x_1, \ldots, x_n)$, $\vec{p}=(r_1,\ldots,r_n,b_{11},\ldots,b_{nn})$, and $F_i = r_i x_i + \sum_{j=1}^{n} b_{ij} x_i x_j$. The set of all dynamical systems, $\mathcal{D}'$, for a given number of state variables $n$ and a given number of parameters $n'$, is then
\begin{equation}\label{eq:setdynsys}
\mathcal{D}' = \{ (F(-,\vec{p}),\vec{p}) | F \colon \mathbb{R}^n \times \mathbb{R}^{n'} \rightarrow \mathbb{R}^n, \vec{p} \in \mathbb{R}^s \}.
\end{equation}
The space of all possible $F$ may be too large to precisely define probabilities over, in which case it is possible to consider various subspaces $\mathcal{D} \subset \mathcal{D}'$. In some cases these may even be given by parametrized models with a single fixed form of $F$ and then varying $\vec{p}$ alone would be sufficient to vary within that class of dynamical systems.

@@

\subsection{Equivalence classes of systems associated to Jacobian Matrices}
We would ultimately like to determine the probability of a stable system remaining stable in the context of evolution modeled as a stochastic process operating on a large set of dynamical systems. Any given Jacobian matrix, which is what characterizes the stability of a system near a given fixed point, does not refer to a single dynamical system, but rather a set of fundamentally distinct dynamical systems from which that Jacobian matrix could have derived. More precisely, matrices of numbers corresponding to some Jacobian matrix evaluated at some fixed point define an equivalence relation, $\sim$, on the set of fixed points, $\mathcal{F}$, given by $(F,\vec{p},\vec{x}^0) \sim (F',\vec{p}\,',\vec{x}^{0'}) $ if and only if
\begin{equation}\label{eq:jaceqrel}
\left. \frac{\partial F(\vec{x},\vec{p})}{\partial \vec{x}} \right|_{\vec{x} = \vec{x}^0} =
\left. \frac{\partial F'(\vec{x},\vec{p}\,')}{\partial \vec{x}} \right|_{\vec{x} = \vec{x}^{0'}}.
\end{equation}
This relation then partitions the set of all fixed points into equivalence classes $\mathcal{F}/{\sim}$, where the class $[A]$ associated to Jacobian matrix $A \in \mathbb{R}^{n \times n}$ is
\begin{equation}\label{eq:jaceqs}
[A] = \left\{ (F,\vec{p},\vec{x}^0) \; \Bigg| \; \left. \frac{\partial F(\vec{x},\vec{p})}{\partial \vec{x}} \right|_{\vec{x} = \vec{x}^0} = A \right\}.
\end{equation}
An example with two members of $\mathcal{F}$ from each of four different equivalence classes $[A_1]$, $[A_2]$, $[A_3]$, and $[A_4]$ of $\mathcal{F}/{\sim}$ is shown in \ref{fig:robustnessconcept}.

% \subsection{Overview}
\subsection{Interaction graphs encoding network architecture}
We are interested in the manner in which system variables interact with one another, and, ultimately, whether dynamical robustness depends upon the topology of these interactions. Interactions among system variables can be encoded in a directed graph associated to the system. Strictly speaking, the interactions among variables in a dynamical model for any network can be represented in terms of a global interaction graph (\ref{fig:biomodelexamples} top row).
For a general system $X \in \mathcal{D}$ the directed graph $G_X$ that describes the manner in which each of the variables depends upon one another can be represented by the adjacency matrix $\adj(G_X)$ where $\adj(G_X)_{ij}$ is $1$ if $F_i \hbox{ depends on } x_j$ and $0$ if $F_i \hbox{ does not depend on } x_j$. These two conditions on global system interactions are expressed locally for all $\vec{x}$ in terms of elements of the Jacobian matrix as $\frac{\partial F_i}{\partial x_j}(\vec{x}) \neq 0$ and $\frac{\partial F_i}{\partial x_j}(\vec{x}) = 0$.
%  \begin{displaymath}
%    \adj(G_X)_{ij} = \left\{
%      \begin{array}{ll}
%        1, & F_i \hbox{ depends on } x_j\\
%        0, & F_i \hbox{ does not depend on } x_j
%      \end{array}.
%    \right.
% \end{displaymath}
For large systems, since any given variable is only likely to interact with a relatively small proportion of the other variables, these matrices may be sparse.
We can also associate a local interaction graph $G_A$ given by an adjacency matrix $\adj(G_A)$ to each dynamical system having Jacobian matrix $A$ at some fixed point $\vec{x}^0$ where
 \begin{equation}\label{eq:lininterdepadj}
   \adj(G_A)_{ij} = \left\{
     \begin{array}{lr}
       1, & a_{ij} \neq 0\\
       0, & a_{ij} = 0
     \end{array}.
   \right.
\end{equation}
In general, the graph $G_A$ is a subgraph of $G_X$, however, for the classes of systems of interest here, $G_A$ is equal to $G_X$, and thus $\adj(G_A) = \adj(G_X)$ (see \refsupp{} \ref{sec:reactionnetjacobian}). We define the connectivity to be equal to the number of edges in $G_A$, which is equivalent to summing up the number of non-zero entries of $\adj(G_A)$.
These interaction graphs can be viewed as deriving from the combination of system components that accept a given pattern of inputs and produce a given pattern of outputs (\reffigexamplesystemmodules).

@@

\section{Evolutionary processes sampling dynamical systems}
In the course of biological evolution, the parameter values $\vec{p}$, form of the functions $F$, and environmental conditions restricting access to the basins associated to different fixed points $\vec{x}^0$ corresponding to all different types of networks considered in \ref{fig:biomodelexamples} are subject to, potentially drastic, modifications due to environmental fluctuations. The stochastic process by which these modifications occur induces a process on the set of fixed points that results in the assignment of a probability $P(f^T)$ to each history of length $T$, $f^T = ( f_1,f_2,\ldots,f_T ) \in \mathcal{F}^T$ \cite{RobertM.Gray130}.
% $$
% P(f',t+1 | f,t) = \mathcal{T}_{\mathcal{F}}(f',f)
% $$
% for all $f,f' \in \mathcal{F}$.
These dynamics induce a stochastic process on the equivalence classes of fixed points $\mathcal{F}/{\sim}$ indexed by Jacobian matrices given by
$$
P([A]^T) = \sum_{ \{ f^T \mid f_i^T \in [A]_i^T \} } P(f^T)
$$
for each history of length $T$, $[A]^T = ( [A_1], [A_2], \ldots, [A_T] ) \in (\mathcal{F}/{\sim})^T$
% $$
% P([A'],t+1 | [A],t) = \mathcal{T}_{\mathcal{F}/{\sim}}([A'],[A])
% $$
% for all $A,A' \in \mathcal{F}/{\sim}$
as visualized in \ref{fig:robustnessprocess}B. These changes can alter the stability of a given system, thereby inducing an even more coarse-grained stochastic process on the stable regions of the space of fixed points given by
$$
P(s^T) = \sum_{ \{ A^T \mid \mathcal{S}(A_i^T) = s_i^T \} } P(A^T)
$$
for each history of length $T$, $s^T = ( s_1, s_2, \ldots, s_T ) \in \{0,1\}^T$ where $s=1 \equiv S,\, s=0 \equiv U$ as visualized in \ref{fig:robustnessprocess}A and B. In order to model this, we consider a process whereby perturbations applied to a given dynamical system and fixed point associated to a stable Jacobian matrix $A$ lead to another Jacobian matrix $A'$.  This corresponds to an ensemble of fixed points of dynamical systems where each model in the ensemble may otherwise be defined in terms of a different collection of rate functions $F'$, vector of parameters ${\vec{p}}\,'$, or environmental conditions restricting access to $\vec{x}^{0'}$ (\refsupp{} \ref{sec:reactionnetjacobian}). We then ask what is the probability, given $A$ is a stable matrix, that $A'$ is also a stable matrix. This quantifies the intuitive statement that, over evolutionary timescales, it is not enough for a system to be stable, but rather that it have a reasonably high probability of remaining stable over contiguous timeframes. In terms of a history $s^T$ over the states specifying the stability property, $\mathcal{S}$, this is given by
$$
r = \frac{\sum_{t=0}^{T-1} s_{t+1}^T s_{t}^T}{\sum_{t=0}^{T-1} s_{t}^T}.
$$
If the process $P(s^T)$ has limits $\mu(s) = \lim_{t,T \rightarrow \infty} P(s_t^T=s)$ and $\tau(s' \mid s) = \lim_{t,T \rightarrow \infty} P(s_{t+1}^T = s' \mid s_t^T = s)$ for $s,s' \in \{0,1\}$
%stationary probability $P^{\infty}(s)$ for $s \in \mathcal{S}$
, the expectation of $r$ as $T \rightarrow \infty$ is approximated by
\begin{equation}\label{eq:robustnessfromstoch}
R(S,\mu,\tau) = E[r] \approx \frac{\sum_{s,s'} \mu(s) \tau(s' \mid s)}{\sum_{s=1} \mu(s)}.
\end{equation}
This conditional probability corresponds to the parameter $R$ of the two-state process depicted in \ref{fig:robustnessprocess}A, and it is what we refer to as dynamical robustness.

@@

\subsection{Symmetries of SCCs and their relationship to robustness}
This map $\hier$ is many-to-one and so there is a large class of
operations which leaves $\hier(G)$ invariant for a given graph $G$, \reffighiertransformations{}. These three symmetries, \reffigscc{}, represent transformations that can be performed on the interaction graph that do not change the network of SCCs to which it is associated.
For instance, we may interchange the positions of the SCCs relative to each other \reffighiertransformations$a$.  Leaving the components fixed, we may move links between nodes in a component \reffighiertransformations$b$ or between components, or even add or delete links \reffighiertransformations$c$.

Symmetries with respect to some property of the system are characterized by the ability to interchange these modules or their connectivity without changing that property. Two of these three intrinsic symmetries of $\hier$ are also symmetries with respect to dynamical robustness. \ref{fig:robustnesssymmetries} shows an example of these latter symmetries applied to a specific interaction graph. The collections of networks that have equivalent dynamical robustness characterized by its symmetries allow for a classification of neutral networks with respect to any evolutionary process selecting for dynamical robustness.

\section{Derivation of the relationship between network architecture and robustness}
Here we show that dynamical robustness is maximized by the most hierarchical of network architectures. In doing so, we restrict to a set of networks that has the same SCCs but may have different number and connectivity of links between the components, consider a stochastic process as a simple model for evolution that independently resamples individual elements of Jacobian matrices, and maximize robustness in that context.

We demonstrate that the Jacobian matrix associated to a system at a fixed point is stable in the sense of \ref{eq:stabeval} if and only if each of the blocks corresponding to its SCCs are all independently stable. We derive an analytical expression for dynamical robustness, $R$, of a network in terms of its interaction graph, $G$, as a weighted average of the dynamical robustness values, $R_{\alpha}$, of the SCCs, $C_{\alpha}$, the corresponding number of links within each SCC, $d_{\alpha}$, and the number of links between the SCCs, $l$ to give a total connectivity $d = l + \sum_{\alpha} d_{\alpha}$. For a given collection of SCCs, we show that the network architectures maximizing dynamical robustness must maximize the number of links between those SCCs. The latter corresponds to the most hierarchical network architecture that can be constructed from that set of SCCs.
%The network architecture having $l=l_{max}$ is the most hierarchical one. Comparing the robustness of a network architecture having $l = l_{max}$ to any other network architecture having any other value of $l$, we show that the network architecture having $l = l_{max}$ maximizes dynamical robustness.
These results ultimately hold for those processes involving simultaneous perturbation of any number of elements of the Jacobian. To anchor the intuition before stating the more general result, we derive the expression for the case of perturbing a single element at each timestep of the stochastic process being used as a simplistic model of evolution.

\subsection{Decomposition of stability over SCCs}
Let the index $i$ range over the non-zero entries $a_i$ of $A$. The entries of the Jacobian are sampled independently from a generic probability distribution $\rho_i$ for each entry. Under this assumption then
\begin{equation}\label{eq:singleresamplemutau}
\begin{aligned}
\mu(A) &= \prod_i \rho_i(a_i),\\
\tau^{(1)}(A' \mid A) &= \frac{1}{d} \sum_i \tau^{(1)}_i (A' \mid A),
\end{aligned}
\end{equation}
where
$$
\tau^{(1)}_i(A' \mid A) = \rho_i(a'_i) \prod_{j \neq i} \delta(a'_j - a_j).
$$
